Article Title

### 2013-09-30 sections/Estimators.tex
minor

For Gaussian Graphical Models, zeros in the inverse covariance matrix indicate statisitcal independence between the corresponding pairs. Thus the inverse covariance matrix is also the adjacency matrix of the graphical model, indicating which pairs are conditionally dependent. \TODO{discuss how quickly (or slowly) this breaks down with deviations from gaussianity, e.g.~MaxEnt models, Ising models.} \TODO{Also, motivate this from the perpsective of linear regression as in \cite{Varoquaux:2012}.} \TODO{Relate to partial pairwise correlations.} Regularization of covariance matrix estimation by sparsifying the inverse of the estimate has been using in function genomics \cite{Schafer:2005,other} and fMRI functional connectivity \cite{Varoquaux:2012}.

>>>>

For Gaussian Graphical Models, zeros in the inverse covariance matrix indicate statisitcal independence between the corresponding pairs. Thus the inverse covariance matrix is also the adjacency matrix of the graphical model, indicating which pairs are conditionally dependent. \TODO{discuss how quickly (or slowly) this breaks down with deviations from gaussianity, e.g.~MaxEnt models, Ising models.} \TODO{Also, motivate this from the perpsective of linear regression as in \cite{Varoquaux:2012}.} \TODO{Also relate to partial pairwise correlations.} Regularization of covariance matrix estimation by sparsifying the inverse of the estimate has been using in function genomics \cite{Schafer:2005,other} and fMRI functional connectivity \cite{Varoquaux:2012}.
